Kindly Bent to Free Us

### 2019-07-11 kindly/soa.tex

>>>>

\citet{DBLP:journals/corr/abs-1803-02796} presents
an extension of OCaml for resource management in the style of C++'s RAII
and Rust's lifetimes. This system assumes
the existence of a linear type system and develop the associated compilation
and runtime infrastructure. We believe our approaches are very
complementary and aim to combine them in the future.
